Choosing a Population Genomics Approach

### 2021-12-17 choosing-population-genetics.Rmd
popgen approach changes

It should be noted that you don’t need to choose only one approach for all samples! If you are starting a research program on a species without any genomic resources, you may want to start with denovo RADseq to understand basic population structure and genetic diversity, then once a reference genome is assembled move to high/low coverage WGS.In the [MarineOmics seminar](https://marineomics.github.io/panels.html), Misha Matz recommended choosing one individual to use for genome assembly, doing high coverage WGS on a few other individuals that represent most of the variation in your taxa, and then WGS many other individuals at low coverage. The high coverage individuals can be useful for imputing missing genotypes in the low coverage samples.

>>>>

It should be noted that you don’t need to choose only one approach for all samples! If you are starting a research program on a species without any genomic resources, you may want to start with denovo RADseq to understand basic population structure and genetic diversity, then once a reference genome is assembled move to high/low coverage WGS.In the [MarineOmics seminar](https://marineomics.github.io/panels.html), [Misha Matz](https://matzlab.weebly.com/) recommended choosing one individual to use for genome assembly, doing high coverage WGS on a few other individuals that represent most of the variation in your taxa, and then WGS many other individuals at low coverage. The high coverage individuals can be useful for imputing missing genotypes in the low coverage samples.
